Run models

### 2017-01-30 Code/3_validation/run-models.Rmd

```{r fit_models_alabama_males}
#run time: expect 2 hours
#fit the bayesian models and put the 1000 posterior samples into a data frame

list_set2 <- list("Colorado", "Connecticut", "Delaware", "Washington DC", "Florida", "Georgia") #saved as results_set_2

system.time(
  for(sex_i in c("Male", "Female")){
    #for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) { #saved as results_set_1
    for(state_i in c("Colorado", "Connecticut", "Delaware", "Washington DC")) { #saved as results_set_2
      assign(paste0("r.White.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))
    }
  }
)

@@

```{r save_results}

#SET 1: Alabama, Arizona, Arkansas, California
save(r.All, le.calculations, file = "~/BW_results/results_set_1.Rdata") 
write.csv(x = BlackWhite, file = "~/BW_results/BlackWhite_set_1.csv")
write.csv(x = age.decomp.estimates, file = "~/BW_results/age_decomp_set_1.csv")
write.csv(x = cod.marginal.estimates, file = "~/BW_results/cod_marginal_set_1.csv")
write.csv(x = age.cod.estimates, file = "~/BW_results/age_cod_set_1.csv")
```

>>>>

```{r fit_models_alabama_males}
#run time: expect 2 hours
#fit the bayesian models and put the 1000 posterior samples into a data frame
system.time(
  for(sex_i in c("Male", "Female")){
    #for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) { #saved as results_set_1
    for(state_i in c("Colorado", "Connecticut", "Delaware", "Washington DC")) { #saved as results_set_2
      assign(paste0("r.White.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))
    }
  }
)

@@

```{r save_results}
#SET 1: Alabama, Arizona, Arkansas, California
# save(r.All, le.calculations, file = "~/BW_results/results_set_1.Rdata") 
# write.csv(x = BlackWhite, file = "~/BW_results/BlackWhite_set_1.csv")
# write.csv(x = age.decomp.estimates, file = "~/BW_results/age_decomp_set_1.csv")
# write.csv(x = cod.marginal.estimates, file = "~/BW_results/cod_marginal_set_1.csv")
# write.csv(x = age.cod.estimates, file = "~/BW_results/age_cod_set_1.csv")

#SET 2: Colorado, Connecticut, Delaware, Washington DC
save(r.All, le.calculations, file = "~/BlackWhiteMortalityGap/Results/results_set_2.Rdata") 
write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_2.csv")
write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_2.csv")
write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_2.csv")
write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_2.csv")
```
